---
title: "Homework 10"
author: "Sparhawk"
date: "2023-04-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework 10




## Question the First

"Using a for loop, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use return(counter) for the output."

```{r}
zeroCount <- function(x=runif(10)) {
  count <- 0
  for (i in seq_along(x)) {
    if (x[i]==0) {
      count <- count + 1
    }
  }
  return(count)
}

# testing
x <- c(0,0,0,7,4,40,200) # 5 zeros
print(zeroCount(x))
```

## Question the Second

"Ok now code that with subsetting to be one line, like a boss"

```{r}
# FUNCTION: zeroCount2 #########################
# packages: none
# purpose: count the number of zeroes in a vector
# input: a numeric vector
# output: a single integer
# 
zeroCount2 <- function(x=runif(10)) {
  count <- length(x[x %% 10 == 0])
  return(count)
}

# testing
print(zeroCount2(x))

```
Technically this one only counts numbers like 200 as having one zero, and numbers like 3053 as having none. I could make more complex code to do that, but it would be more than one line (or a VERY long one). The point is; voila, subsetting!


## Question the Third!

"Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number."

```{r}
# FUNCTION: productMatrix #########################
# packages: none
# purpose: create a matrix of the products of the row and column numbers
# input: the row and column lengths of a matrix
# output: a matrix
# 
productMatrix <- function(rows=5, columns=4) {
  m <- matrix(data = NA,nrow=rows,ncol=columns)
  for (i in 1:rows) {
    for (j in 1:columns) {
      m[i,j] <- i*j # these would be a vector[i]*vector[j] if the inputs were vectors
    } 
  } 
  return(m)
}
# test
print(productMatrix())
```

## Question the Fourfvth!

### a. Make a data frame with 3 groups of data with different means

```{r}
groups <- c(rep("Control",100),rep("Treatment1",100),rep("Treatment2",100))
data <- c(rnorm(100,mean = 7, sd = 3),
          rnorm(100,mean = 10, sd = 2),
          rnorm(100,mean = 20, sd = 4))
John <- data.frame(groups,data)

head(John)
```


### b. Reshuffle the response varaible and calculate the means of each group (in one function)

```{r}
# FUNCTION: shuffle_and_means #########################
# packages: none
# purpose:  
# input: 
# output: 
# 
shuffle_and_means <- function(df=NULL) {
  if(is.null(df)) {stop("gimme a data frame or fugeddaboutit") }
  
  df[,2] <- sample(df[,2])
  
  means <- c(mean(df$data[1:100]),mean(df$data[101:200]),mean(df$data[201:300]))
  # wish I remembered how to select by another column's values
  
  return(means)
}
# test
print(shuffle_and_means(John))
```


### c. use a for loop to repeat shuffle_and_means 100 times in a data frame.

```{r}
# Data frame for means storage
meanDF <- matrix(data = NA, nrow = 100, ncol = 4, )
meanDF <- data.frame(meanDF)

library(tidyverse)
meanDF <- rename(meanDF,replication=X1, ControlAvg=X2, Treat1Avg=X3, Treat2Avg=X4)

# for loop:
for (i in 1:100) {
  meanDF[i,] <- c(i,shuffle_and_means(John))
}
head(meanDF)
```

### d. make a histogram of the reshuffled group means

```{r}
# simple plot
qplot(meanDF$ControlAvg) 

# overlayed histograms
ggplot(meanDF,mapping=aes(x=ControlAvg)) + # this changes the x-axis labels...
  geom_histogram(fill="black", color="black",alpha=0.2) +
  geom_histogram(aes(x=Treat1Avg), fill="blue",color="black",alpha=0.4) +
  geom_histogram(aes(x=Treat2Avg), fill="red",color="black",alpha=0.4)
# I'm sure I could spend another 15 minutes looking up how to set up a legend and correct axis labels...
# but you see the gist! Data: graphed.
```
