---
title: "Homework12"
author: "Sparhawk"
date: "2023-04-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework 12:
## The GooGoo Plots Greatest Hists

Libraries and data
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(patchwork)

# Full Data:
Full <- read.csv("CleanedData.csv")
```

### Making a Scatterplot of Callback Return Rate vs. Attractiveness

First choose and organize the data
```{r}
# Callbacks by photo ----------------------------------------------

# getting unique photos and rating organized
df <- dplyr::select(Full, photo, avg_rating) %>%
  arrange(photo) %>%
  unique()

# for loop vectors setup
Callbacks <- c()
Attempts <- c()
Photo <- c()

# getting callbacks, applications, and return rate per photo
for (i in 1:length(unique(Full$photo))) {
  Attempts <- c(Attempts,nrow(Full[Full$photo==i,]))
  Callbacks <- c(Callbacks,nrow(Full[Full$photo==i & Full$callback==1,]))
  Photo <- c(Photo,i)
}

# Build the Data Frame
CBDF <- data.frame(Photo,df$avg_rating, Attempts,Callbacks) %>%
  mutate(Return = Callbacks/Attempts) %>%
  rename(Attractiveness = df.avg_rating)
head(CBDF)
```

Now let's make a very simple scatterplot
```{r}
# Graph: Simple Scatterplot

s1 <- ggplot(data=CBDF) +
  aes(x=Attractiveness, y=Return) +
  geom_point() # +
   # geom_text(label=Photo,
   #          nudge_x = 0.1, 
   #          size=2,
   #          check_overlap = T))

print(s1)
```
As you can see I included the code to add labels. They're not so useful in this plot, but it's good to have the option.

### Make a scatterplot for men and women

Rather than doing the whole dataframe creation process over again (I could), I happen to know which ones are male and which are female, so I'll just divide it manually.
```{r}
# manual Dataframe division
CBDF$Gender <- c(rep("Woman",32),rep("Man",32))


# scatterplot with color ~and~ shape changes
s1 <- ggplot(data=CBDF) +
  aes(x=Attractiveness, y=Return,
      color=Gender,
      shape=Gender) +
  geom_point()

print(s1)

# scatterplot with total applications as dot size
s2 <- ggplot(data=CBDF) +
  aes(x=Attractiveness, y=Return,
      color=Gender,
      shape=Gender,
      size=Attempts,
      alpha=0.75) + # transparency for clarity
  geom_point()

print(s2)
```


### Mirrored Histogram of Attractiveness

```{r}
# Setup simpler, more convenient dataframe:
AbyG <- data.frame(Female = CBDF$Attractiveness[1:32],
                   Male=CBDF$Attractiveness[33:64])
# this makes the mirroring a lot easier, I've found

  
# Junior Double Triple Histogram
h <- ggplot(data=AbyG)+
  aes(x=x)+
  geom_histogram( aes(x=Female,y=..density..),
                  binwidth = 0.25,
                  fill="pink",color="black") +
  # Men
  geom_histogram( aes(x=Male,y=-..density..),
                  binwidth=0.25,
                  fill="aquamarine",color="black")


# or a density funciton, same diff
d <- ggplot(data=AbyG)+
  aes(x=x)+
  geom_density( aes(x=Female,y=..density..),
                  fill="pink",color="black") +
  # Men
  geom_density( aes(x=Male,y=-..density..),
                  fill="aquamarine",color="black")

#print
print(h)
print(d)
```